Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-04 paper.tex
gq on abstract
Remove a line
gq on a paragraph
Remove a joke

Much research is currently being done to study how non-volatile and large memory
    systems would change system design.  We see the need for a lightweight tool
    to study such systems at scale with real workloads.  The first step towards
    building such a tool is to study the scalability of existing memory
    management systems.

We find that in most cases, Linux kernel memory management scales well with
    large amounts of physical memory. However, workloads that allocated many
    virtual memory areas can accumulate significant memory and computational
    overhead due to kernel metadata.     
    Furthermore, in certain situations, transparent hugepages can nullify the
    benefits from better TLB reaches by inducing memory pressure earlier, even
    for workloads that would otherwise not experience it.

Finally, we see that the 99.99-th percentile of disk latency during swapping
    can account for over 70\% of runtime for the workloads we tested.

@@

The emergence of the internet required businesses to buy expensive machines to
keep up with demand for their services, but systems researchers did not have
access to these machines. Alameldeen et al. describe how they simulate a
multi-million dollar server using a \$2000 workstation. To do this, they go
through several rounds of scaling down, optimizing, changing, and tuning both
the benchmarks and systems they test. For example, they scale down a workload to
fit in the 1GB memory of the machine they use and increase the number of threads
to improve parallelism \cite{2kmachine}. This methodology may be accurate, but
it requires modifying the benchmarks, which is error prone and time consuming;
it can be extremely difficult to validate changes to a benchmark. Ideally,
researchers can run large experimental workloads without changes, but the overheads
of current memory management systems prevent this from being practical.

@@

Two threads walk into a bar. Bartender Hasnain looks up and yells, ``Hey, I want
don’t any conditions race like time last!''

>>>>

Much research is currently being done to study how non-volatile and large
memory systems would change system design.  We see the need for a lightweight
tool to study such systems at scale with real workloads.  The first step
towards building such a tool is to study the scalability of existing memory
management systems.  We find that in most cases, Linux kernel memory management
scales well with large amounts of physical memory. However, workloads that
allocated many virtual memory areas can accumulate significant memory and
computational overhead due to kernel metadata.     Furthermore, in certain
situations, transparent hugepages can nullify the benefits from better TLB
reaches by inducing memory pressure earlier, even for workloads that would
otherwise not experience it.  Finally, we see that the 99.99-th percentile of
disk latency during swapping can account for over 70\% of runtime for the
workloads we tested.

@@

The emergence of the internet required businesses to buy expensive machines to
keep up with demand for their services, but systems researchers did not have
access to these machines. Alameldeen et al. describe how they simulate a
multi-million dollar server using a \$2000 workstation. To do this, they go
through several rounds of scaling down, optimizing, changing, and tuning both
the benchmarks and systems they test. For example, they scale down a workload
to fit in the 1GB memory of the machine they use and increase the number of
threads to improve parallelism \cite{2kmachine}. This methodology may be
accurate, but it requires modifying the benchmarks, which is error prone and
time consuming.  Ideally, researchers can run large experimental workloads
without changes, but the overheads of current memory management systems prevent
this from being practical.

@@

%Two threads walk into a bar. Bartender Hasnain looks up and yells, ``Hey, I want
%don’t any conditions race like time last!''
